The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2020-03-31 Paper/jaccardbaetica.tex
add bib

Finally, The increase in olive oil exports would experience a progressive slowdown
from the third century A.D., coinciding with the change in market strategy in the
Empire. As a result, a progressive decrease of Dressel 20 is documented being gradually replaced for Dressel 23 amphorae. \maria {citation needed}

@@

However, the Roman studies about the presence of Dressel 20 amphorae in textit{Germania} has not had the same repercussion as the rest of the province. This could be explained due to the lack of archaeological sources citep{horacio2010llegada}.

@@

In \textit{Germania}, the results followed the same pattern as \textit{Britannia} but with a minor correlation as we can observe in the dendrogram. The areas mostly militarised share similar stamps than civil areas. However, we do not detect a concrete pattern regarding the distribution of the stamps in the German limes. \maria{citar remesal xanten}.

@@

On the other hand,the existence of different stamps in the same workshop but which are only repeated in very close places it would imply some kind of organisation from within workshop affecting the closest centres. This could be interpreted such as batch systematic organisation between potters \maria{citar tesis de moros}. 
This method allowed to potters organise the production with the batch stamping for the posterior commercialisation.

>>>>

Finally, The increase in olive oil exports would experience a progressive slowdown
from the third century A.D., coinciding with the change in market strategy in the
Empire. As a result, a progressive decrease of Dressel 20 is documented being gradually replaced for Dressel 23 amphorae \citep{rodriguez1991aceite,
millet_anforas_1998}.

@@

However, the Roman studies about the presence of Dressel 20 amphorae in textit{Germania} has not had the same repercussion as the rest of the province. This could be explained due to the lack of archaeological sources \citep{horacio2010llegada}.

@@

In \textit{Germania}, the results followed the same pattern as \textit{Britannia} but with a minor correlation as we can observe in the dendrogram. The areas mostly militarised share similar stamps than civil areas. However, we do not detect a concrete pattern regarding the distribution of the stamps in the German limes \citep{xanten2018}.

@@

On the other hand,the existence of different stamps in the same workshop but which are only repeated in very close places it would imply some kind of organisation from within workshop affecting the closest centres. This could be interpreted such as batch systematic organisation between potters \citep{juanmorostesis}. 
This method allowed to potters organise the production with the batch stamping for the posterior commercialisation.
